---
title: "The Machine Learning of Sperm DDE Exposure"
author: "Hyeyeon Hwang"
date: "May 30, 2019"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries
```{r, echo=TRUE, results='hide', message=FALSE}
# Load libraries
library(knitr)
library(kableExtra)

library(tidyverse)
library(caret)
library(e1071) # for train
library(randomForest) # for RF model
library(kernlab) # for SVM model

library(Boruta) # for RF feature selection
library(sigFeature) # for SVM feature selection 
```
If the R package, package_name, is not already installed,
use ```install.packages("package_name")``` to before loading package with ```library(package_name)```

If the `sigFeature` is not already installed, use the following code to install it before loading the package with ```library(sigFeature)```

```
# To install "sigFeature": 
if (!requireNamespace("BiocManager", quietly = TRUE))
   install.packages("BiocManager")
# # The following initializes usage of Bioc devel
BiocManager::install(version='devel')
BiocManager::install("sigFeature")
```

# R Markdown

```{r cars}
summary(cars)
```

# Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
